A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-12 05_calibration_data.Rmd
combine smooth and thin

# now apply the smooth
data <- atl_median_smooth(data = data,
                          x = "x", y = "y", time = "time",
                          moving_window = 5)
```

```{r echo=FALSE}
# make zoomed in figures
fig_inset <- mapply(function(xl, yl) {
  ggplot()+
    geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
               aes(x, y),
               col = "grey",
               shape = 4,
               size = 0.4)+
    geom_point(data = data_unproc,
               aes(x, y),
               col = pal[3],
               shape = 19, 
               alpha = 0.5)+
    geom_path(data = data,
              aes(x, y),
              col = RColorBrewer::brewer.pal(4, "Set1")[4])+
    ggthemes::theme_few()+
    theme(axis.title = element_blank(),
          axis.text = element_blank())+
    ggspatial::annotation_scale(location = "br")+
    coord_cartesian(
             xlim = xl,
             ylim = yl, expand = F
             )+
    labs(colour = "track")
}, list(xl1 = c(650785, 653250),
        xl2 = c(650045, 650682)),
   list(yl1 = c(5904450, 5906133),
        yl2 = c(5902700, 5903080)),
SIMPLIFY = FALSE)

# # add global figure to second inset
# fig_inset[[2]] <- fig_inset[[2]] +
#   annotation_custom(grob = ggplotGrob(fig_smooth),
#                     xmin = 649990,
#                     xmax = 650045 + (650682 - 650045)/2,
#                     ymin = 5903080 - (5903080 - 5902700)/2.5,
#                     ymax = 5903080
#                     )

fig_median_smooth <- fig_inset[[1]]
  # wrap_plots(fig_inset)+
  # plot_annotation(tag_levels = "a",
  #                 tag_prefix = "(",
  #                 tag_suffix = ")")
# save figure
ggsave(fig_median_smooth,
       filename = "figures/fig_calib_median_smooth.png",
       width = 90 / 25, height = 90 / 25)
```

@@

```{r echo=FALSE}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_data_bbox, fig_speed_outliers, fig_median_smooth),
  design = "AB\nAC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")&
  theme(plot.tag = element_text(face = "bold"))

# save combined figure
ggsave(figure_walkthrough,
       filename = "figures/fig_walkthrough.png",
       height = 130, width = 170, units = "mm")
```

@@

## Making residence patches

@@

```{r}
# load recurse
library(recurse)
data_recurse <- data_unproc[, list(x, y, time, TAG, UTCtime)]

# thin the data
data_recurse <- atl_thin_data(data = data_recurse,
                              interval = 30, id_columns = "TAG",
                              method = "resample")

# get 4 column data
data_recurse <- data_recurse[, list(x, y, time, TAG)]

>>>>

# now apply the smooth
atl_median_smooth(data = data,
                  x = "x", y = "y", time = "time",
                  moving_window = 5)
```

### Plot smoothed data

```{r}
# make zoomed in figures
fig_smooth <-
  ggplot()+
  geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
             aes(x, y),
             col = "grey",
             shape = 4,
             size = 0.4)+
  # smoothed data
  geom_path(data = data_unproc,
             aes(x, y),
             col = pal[3]) +
  geom_point(data = data_unproc,
             aes(x, y),
             col = pal[3],
             shape = 19,
             alpha = 0.5) +
  coord_cartesian(
    xlim = c(650785, 653250),
    ylim = c(5904450, 5906133), 
    expand = F
  )+
  ggthemes::theme_few()+
  theme(axis.title = element_blank(),
        axis.text = element_blank())+
  ggspatial::annotation_scale(location = "br")

ggsave(fig_smooth,
       filename = "figures/fig_calib_median_smooth.png",
       width = 90 / 25, height = 90 / 25)
```

## Thinning the data

```{r}
# save a copy
data_unproc <- copy(data)

# remove columns we don't need
data <- data[, setdiff(colnames(data), 
                       c("tID", "Timestamp", "id", "TIME", "UTCtime")), 
             with = FALSE]

# thin to a 30s interval
data_thin <- atl_thin_data(data = data,
                           interval = 30,
                           method = "aggregate",
                           id_columns = "TAG")
```

### Plot thinned data

```{r echo=FALSE}
# make zoomed in figures
fig_smooth_thin <-
  ggplot()+
  geom_errorbar(data = data_thin,
                aes(x, y,
                    ymin = y - VARY,
                    ymax = y + VARY),
                col = pal[4],
                alpha = 0.2,
                lwd = 0.1)+
  geom_errorbarh(data = data_thin,
                 aes(x, y,
                     xmin = x - VARX,
                     xmax = x + VARX),
                 col = pal[4],
                 alpha = 0.2,
                 lwd = 0.1)+
  geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
             aes(x, y),
             col = "grey",
             shape = 4,
             size = 0.4)+
  geom_point(data = data_unproc,
             aes(x, y),
             col = pal[3],
             shape = 19,
             alpha = 0.5) +
  geom_point(data = data_thin,
             aes(x, y),
             col = pal[4],
             shape = 1)+
  geom_path(data = data_thin,
            aes(x, y),
            col = pal[4], size = 0.2)+
  coord_cartesian(
    xlim = c(650785, 653250),
    ylim = c(5904450, 5906133), 
    expand = F
  )+
  ggthemes::theme_few()+
  theme(axis.title = element_blank(),
        axis.text = element_blank())+
  ggspatial::annotation_scale(location = "br")

ggsave(fig_smooth_thin,
       filename = "figures/fig_calib_smooth_thin.png",
       width = 90 / 25, height = 90 / 25, dpi = 300)
```

@@

```{r echo=FALSE}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_speed_outliers, fig_smooth_thin),
  design = "A\nB")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")&
  theme(plot.tag = element_text(face = "bold"))

# save combined figure
ggsave(figure_walkthrough,
       filename = "figures/fig_walkthrough.png",
       height = 170, width = 90, units = "mm")
```

@@

```{r}
# load recurse
library(recurse)
data_recurse <- data[, list(x, y, time, TAG)]

# thin the data
data_recurse <- atl_thin_data(data = data_recurse,
                              interval = 30, id_columns = "TAG",
                              method = "resample")
```

## Residence patches

@@

```{r}
# get 4 column data
data_recurse <- data_recurse[, list(x, y, time, TAG)]
